---
title: "Experiment 3 (self-paced reading)"
output: pdf_document
---
\large{R code to reproduce the analysis of Experiment 3 reported in the manuscript \emph{"Does case marking affect agreement attraction in comprehension?"}.} 

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.path='figures/fig-',
               fig.align='center',
               fig.show='hold',warning=FALSE,message=FALSE, echo = FALSE)

```

```{r load_data}
# Load packages
library(dplyr)
library(knitr)
library(kableExtra)
library(brms)
library(MASS)
library(ggplot2)
library(binom)
library(boot) # for backtransformations
library(ggpubr)
library(brmstools)
library(rstanarm)
library(bayesplot)


# Define functions
# Function to calculate standard error.
se <- function(x) {
    return(sqrt(var(x,na.rm=TRUE)/length(na.omit(x))))
}

# Function to calculate binomial standard error.
se.bin <- function(x){
  n.success = sum(na.omit(x)) #x is coded as 1 (success) or 0 (failure), so number of successes is the sum of x = 1 
  n         = length(na.omit(x))
  p         = n.success / n
  return(sqrt(p*(1-p)/n))
}


# Load data
d <- read.csv("E3_data.csv", encoding="UTF-8", header=T)
```

# Participants 
***Participant exclusion.*** In total 120 participants were recruited, but three participants were excluded because their primary language was Russian. As a result, data from 117 were included in the analysis.

```{r}
d <- subset(d, !(subj %in% c(22,43,65))) # exclude participants
```

```{r}
# Summarize demographic data in a table
demographic <- d[!duplicated(d$subj),] # leave one row per participant
demographicRel <- demographic[c(9:12, 14:15)] # select columns with relevant info

options(knitr.kable.NA = '') # exclude NAs in the table
kable(summary(demographicRel), 
      booktabs=T, 
      caption="Summary of participants' demographic characteristics after participant exclusion was performed.")  %>%
  kable_styling(latex_options = c("basic", "scale_down", "hold_position")) %>% 
  row_spec(0,bold=TRUE)
```

```{r subset_data}
# Subset data and convert factors
d$subj<-factor(d$subj,levels=unique(d$subj))
d<-subset(d,expt!="practice") # remove practice items

filler<-subset(d, expt=="filler" & pos=="?") # subset filler items
filler$expt<-factor(filler$expt,levels="filler")
filler$accuracy<-as.numeric(as.character(filler$accuracy))

target<-subset(d, expt=="attraction") # subset experimental items
target$cond<-factor(target$cond,levels=letters[1:8])
target$expt<-factor(target$expt,levels="attraction")
```

```{r data_summary, eval=FALSE}
summary(d[,-6]) # exclude the column w/Armenian characters to prevent execution error

```

# Contrast coding 
Note that the term “interference” applies to sentences with singular attractors in grammatical sentences (i.e., "a" and "e") but plural attractors in ungrammatical sentences (i.e., "d" and "h").

***Main effects and interactions***
```{r echo=TRUE}
# Contrasts to evaluate the main effects of case, number interference ('int'),
# sentence grammaticality ('gram'), and their interactions
##      a   b   c   d   e   f   g   h
#case  -1  -1  -1  -1   1   1   1   1 case match is -1, case mismatch is 1
#int    1  -1  -1   1   1  -1  -1   1 no-interference is -1, interference is 1
#gram   1   1  -1  -1   1   1  -1  -1 ungrammatical is -1, grammatical is 1

target$case<-ifelse(target$cond%in%c("a","b","c","d"),-1,1)
target$int<-ifelse(target$cond%in%c("b","c","f","g"),-1,1)
target$gram<-ifelse(target$cond%in%c("c","d","g","h"),-1,1)
target$casexint<-target$case*target$int
target$casexgram<-target$case*target$gram
target$intxgram<-target$int*target$gram
target$casexintxgram<-target$case*target$int*target$gram
```

\newpage 

***Nested comparisons***
```{r echo = TRUE}
# Contrasts to evaluate the main effects of case, number interference ('int'), 
# and their interaction for the grammatical (x_g) and ungrammatical (x_u) 
# sentences separately.
##            a   b   c   d   e   f   g   h
# gram        1   1  -1  -1   1   1  -1  -1 ungrammatical is -1, grammatical is 1
# case_g     -1  -1   0   0   1   1   0   0 case match is -1, case mismatch is 1
# int_g       1  -1   0   0   1  -1   0   0 no-interference is -1, interference is 1
# casexint_g -1   1   0   0   1  -1   0   0

# case_u      0   0  -1  -1   0   0   1   1
# int_u       0   0  -1   1   0   0  -1   1
# casexint_u  0   0   1  -1   0   0  -1   1

target$case_g <- ifelse(target$cond%in%c("a","b"),-1,
                        ifelse(target$cond%in%c("e","f"),1,0))
target$int_g <- ifelse(target$cond%in%c("b","f"),-1,
                       ifelse(target$cond%in%c("a","e"),1,0))
target$casexint_g <- target$case_g*target$int_g
target$case_u <- ifelse(target$cond%in%c("c","d"),-1,
                        ifelse(target$cond%in%c("g","h"),1,0))
target$int_u <- ifelse(target$cond%in%c("c","g"),-1,
                       ifelse(target$cond%in%c("d","h"),1,0))
target$casexint_u <- target$case_u*target$int_u

# Contrasts to evaluate the number interference effect for the grammatical
# sentences but in case match (nominative attractor; attr_nom_g) and 
# case mismatch (accusative attractor; attr_acc_g) conditions separately
##           a   b    e   f
#case-g     -1  -1   1   1 case match is -1, mismatch is 1
#attr_nom_g  1  -1   0   0 no-interference is -1, interference is 1
#attr_acc_g  0   0   1  -1
target$attr_nom_g<-ifelse(target$cond=="a",1,
                          ifelse(target$cond=="b",-1,0))
target$attr_acc_g<-ifelse(target$cond=="e",1,
                          ifelse(target$cond=="f",-1,0))
```

\newpage 
# Filler accuracy 
* Overall accuracy (%) for the filler items
```{r}
filler %>% dplyr::summarize(
  fillerAccuracy = round(100*mean(accuracy, na.rm = TRUE), digits=1),
  fillerSE = round(100*se.bin(accuracy), digits=1))
```

\vspace{0.5cm}

```{r fig.height=4, fig.width=8}
# Compute mean accuracy for each participant for the filler items

fillerAcc_bySubj <- filler %>% 
  group_by(subj) %>% 
  summarize(Filler_accuracy = round(100 *mean(accuracy), digits = 0))

fillerAcc_bySubj$subj<-as.numeric(as.character
                                  (fillerAcc_bySubj$subj))

# Plot mean accuracy for each participant for the filler items
ggplot(fillerAcc_bySubj, aes(x = subj, y = Filler_accuracy )) + 
  geom_point() +
  scale_x_continuous(name="Participants", breaks=seq(1,120,4))  +
  ylab("Accuracy (%)") -> bySubj_fillerPlot

# Add titles
bySubj_fillerPlot + labs(
  title = "Mean accuracy per participant for the filler items",
  subtitle = "Accuracy ranges from 75% to 100%")

# range(fillerAcc_bySubj$Filler_accuracy) 
```

\newpage 

# Target accuracy 
```{r eval=FALSE}
# Sanity check: everything is balanced
xtabs(~subj+cond,targetAcc) 
xtabs(~item+cond,targetAcc)
xtabs(~subj+item,targetAcc) 
```

* Overall accuracy (%) for the experimental items
```{r}
targetAcc<-subset(target,  pos=="?")
targetAcc$accuracy<-as.numeric(as.character(targetAcc$accuracy))

# Compute overall target accuracy
targetAcc %>% dplyr::summarize(
  trgAccuracy = round(100*mean(accuracy, na.rm = TRUE), digits=1),
  trgSE = round(100*se.bin(accuracy), digits=1))
```

```{r}
# Compute mean accuracy for each condition for the experimental items
target_acc_byCond <-targetAcc %>% 
  group_by(cond) %>% 
  summarize(
  trgAccuracy = round(100 *mean(accuracy), digits = 1),
  trgSE =  round(100*se.bin(accuracy), digits=1)
  )

colnames(target_acc_byCond) <- c("Condition", "Accuracy [%]", "SE")
target_acc_byCond <- as.data.frame(target_acc_byCond)
rownames(target_acc_byCond) <- c("case match, grammatical, interference",
                             "case match, grammatical, no-interference",
                             "case match, ungrammatical, no-interference",
                             "case match, ungrammatical, interference",
                             "case mismatch, grammatical, interference",
                             "case mismatch, grammatical, no-interference",
                             "case mismatch, ungrammatical, no-interference",
                             "case mismatch, ungrammatical, interference")

# Present mean accuracy for each condition in a table
target_acc_byCond %>%
  kable(align="c", 
        booktabs = T, 
         linesep = "",
        caption = "Mean accuracy per condition for the experimental items. The term “interference” applies to sentences with singular attractors in grammatical sentences but plural attractors in ungrammatical sentences.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0, bold = TRUE) %>%
  row_spec(4, hline_after= T) %>%
  column_spec(1, width = "22em")
```

\vspace{0.5cm}

```{r fig.height=4, fig.width=8}
# Compute mean accuracy for each participant for the experimental items
targetAcc_bySubj <- targetAcc %>% group_by(subj) %>% 
  summarize(target_accuracy = round(100 *mean(accuracy), digits = 0))

targetAcc_bySubj$subj<-as.numeric(as.character
                                  (targetAcc_bySubj$subj))

# Plot mean accuracy for each participant for the experimental items
ggplot(targetAcc_bySubj, aes(x = subj, y = target_accuracy )) + 
  geom_point() +
  scale_x_continuous(name="Participants", breaks=seq(1,120,4)) +
  scale_y_continuous(name="Accuracy (%)", breaks=seq(0,100,5)) -> bySubj_targetPlot

# Add titles
bySubj_targetPlot + labs(
  title = "Mean accuracy per participant for the experimental items",
  subtitle = "Accuracy ranges from 65% to 98%")

# range(targetAcc_bySubj$target_accuracy)
```

\newpage

# Reading time data 
```{r}
# pre-process RT data/subset
targetRT<-subset(target,pos!="?")
colnames(targetRT)[7]<-"region"
colnames(targetRT)[6]<-"word"

targetRT$region<-factor(targetRT$region)
rcverb<-subset(targetRT,region=="rcv")
rcadv1<-subset(targetRT, region=="rcadv1")
mcverb<-subset(targetRT, region=="mcv")
```

***RT trimming.*** RTs below 200ms and above 8000ms are excluded.
```{r echo=TRUE}
## percent of data points trimmed across all regions
targetTrimmed<-subset(targetRT, rt>200 & rt<8000)
round(100*((dim(targetRT)[1]-dim(targetTrimmed)[1])/dim(targetRT)[1]), digits=1) 

## percent of data points trimmed in the critical region 
rcverb_trimmed<-subset(rcverb, rt>200 & rt<8000)
round(100*((dim(rcverb)[1]-dim(rcverb_trimmed)[1])/dim(rcverb)[1]),digits=2)

## percent of data points trimmed in the post-critical region 
rcadv1_trimmed<-subset(rcadv1, rt>200 & rt<8000)
round(100*((dim(rcadv1)[1]-dim(rcadv1_trimmed)[1])/dim(rcadv1)[1]),digits=2)

```

```{r}
# Create RT boxplots for critical region
op<-par(mfrow=c(1,2) ,pty="m")
boxplot(rt~cond,
        rcverb_trimmed, 
        col=c("grey","black"), 
        border="brown", 
        notch=TRUE, 
        main="Raw RTs in critical region")

boxplot(log(rt)~cond,
        rcverb_trimmed, 
        col=c("grey","black"), 
        border="brown", notch=TRUE, 
        main="Log RTs in critical region")

```

```{r}
# Create RT boxplots for post-critical region
op<-par(mfrow=c(1,2) ,pty="m")
boxplot(rt~cond,
        rcadv1_trimmed, 
        col=c("grey","black"), 
        border="brown", notch=TRUE, 
        main="Raw RTs in post-critical region")

boxplot(log(rt)~cond,
        rcadv1_trimmed, 
        col=c("grey","black"), 
        border="brown", 
        notch=TRUE, 
        main="Log RTs in post-critical region")
```

```{r}
# Compute mean RTs in the critical region for the four conditions
critRT_byCond<-rcverb_trimmed %>% 
  group_by(cond) %>%
  summarize(
  rtMean = round(mean(rt), digits = 0),
  rtSE = round(se(rt), digits = 0)
  )

colnames(critRT_byCond) <- c("Condition", "Mean RT [ms]", "SE")
critRT_byCond <- as.data.frame(critRT_byCond)
rownames(critRT_byCond) <- c("case match, grammatical, interference",
                             "case match, grammatical, no-interference",
                             "case match, ungrammatical, no-interference",
                             "case match, ungrammatical, interference",
                             "case mismatch, grammatical, interference",
                             "case mismatch, grammatical, no-interference",
                             "case mismatch, ungrammatical, no-interference",
                             "case mismatch, ungrammatical, interference")
 
# Present mean RTs in the critical region in a table
critRT_byCond %>%
  kable(align="c", 
        booktabs = T, 
        linesep = "",
        caption = "Mean reading times in the critical region for the four conditions. The term “interference” applies to sentences with singular attractors in grammatical sentences but plural attractors in ungrammatical sentences.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  row_spec(4, hline_after = T) %>%
  column_spec(1, width = "22em")
```

\vspace{0.5cm}

```{r}
# Compute mean RTs in the post-critical region for the four conditions
postCritRT_byCond <- rcadv1_trimmed %>% 
  group_by(cond) %>% 
  summarize(
  rtMean = round(mean(rt), digits = 0),
  rtSE = round(se(rt), digits = 0)
  )

colnames(postCritRT_byCond) <- c("Condition", "Mean RT [ms]", "SE")
postCritRT_byCond <- as.data.frame(postCritRT_byCond)
rownames(postCritRT_byCond) <- c("case match, grammatical, interference",
                             "case match, grammatical, no-interference",
                             "case match, ungrammatical, no-interference",
                             "case match, ungrammatical, interference",
                             "case mismatch, grammatical, interference",
                             "case mismatch, grammatical, no-interference",
                             "case mismatch, ungrammatical, no-interference",
                             "case mismatch, ungrammatical, interference")
 
# Present mean RTs in the post-critical region in a table
postCritRT_byCond %>%
  kable(align="c", 
        booktabs = T, 
        linesep = "",
        caption = "Mean reading times in the post-critical region for the four conditions. The term “interference” applies to sentences with singular attractors in grammatical sentences but plural attractors in ungrammatical sentences.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  row_spec(4, hline_after = T) %>%
  column_spec(1, width = "22em")
```

# Priors 
```{r eval=FALSE}
# This functions shows which parameters need to have priors
get_prior(rt ~ case*int*gram+
              (1+case*int*gram|subj) + 
              (1+case*int*gram|item),
            data = rcadv1_prev_trimmed, family = gaussian()) 
```

```{r echo=TRUE}
# Priors for reading time analysis involving main effects and interactions
priors_three_way <- c(set_prior("normal(0,10)", class="Intercept"),
                 set_prior("normal(0,1)", class="b", coef="case"),
                 set_prior("normal(0,1)", class="b", coef="int"),
                 set_prior("normal(0,1)", class="b", coef="gram"),
                 set_prior("normal(0,1)", class="b", coef="casexint"),
                 set_prior("normal(0,1)", class="b", coef="casexgram"),
                 set_prior("normal(0,1)", class="b", coef="intxgram"),
                 set_prior("normal(0,1)", class="b", coef="casexintxgram"),
                 set_prior("normal(0,1)", class="sd"),
                 set_prior("normal(0,1)", class="sigma"),
                 set_prior("lkj(2)", class="cor"))
```

```{r echo=TRUE}
# Priors for reading time analysis involving nested comparisons to evaluate  
#  the effects of case, number interference, and their interaction within 
# grammatical and ungrammatical sentences separately.
priors_nested<- c(set_prior("normal(0,10)", class="Intercept"),
           set_prior("normal(0,1)", class="b", coef="gram"),
           set_prior("normal(0,1)", class="b", coef="case_g"),
           set_prior("normal(0,1)", class="b", coef="int_g"),
           set_prior("normal(0,1)", class="b", coef="casexint_g"),
           set_prior("normal(0,1)", class="b", coef="case_u"),
           set_prior("normal(0,1)", class="b", coef="int_u"),
           set_prior("normal(0,1)", class="b", coef="casexint_u"),
           set_prior("normal(0,1)", class="sd"),
           set_prior("normal(0,1)", class="sigma"),
           set_prior("lkj(2)", class="cor"))

# Priors for reading time analysis involving nested comparisons to evaluate 
# the effect of number interference for the grammatical sentences but in 
# case match and case mismatch conditions separately. 
priors_nested_g<- c(set_prior("normal(0,10)", class="Intercept"),
           set_prior("normal(0,1)", class="b", coef="case_g"),
           set_prior("normal(0,1)", class="b", coef="attr_nom_g"),
           set_prior("normal(0,1)", class="b", coef="attr_acc_g"),
           set_prior("normal(0,1)", class="sd"),
           set_prior("normal(0,1)", class="sigma"),
           set_prior("lkj(2)", class="cor"))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model to evaluate main effects of case, number interference, sentence grammaticality, and their interactions in the critical region
mrcv <- brm(formula = log(rt) ~ case+int+gram+casexint+casexgram+intxgram+casexintxgram+
              (1+case+int+gram+casexint+casexgram+intxgram+casexintxgram|subj) + 
              (1+case+int+gram+casexint+casexgram+intxgram+casexintxgram|item),
            data = rcverb_trimmed, family = gaussian(), prior = priors_three_way,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model to evaluate main effects of case, number interference, and their interaction in the critical region for the grammatical and ungrammatical sentences separately
mrcv_nested <- brm(formula = log(rt) ~ gram+case_g+int_g+casexint_g+case_u+int_u+casexint_u+
              (1+gram+case_g+int_g+casexint_g+case_u+int_u+casexint_u|subj) + 
              (1+gram+case_g+int_g+casexint_g+case_u+int_u+casexint_u|item),
            data = rcverb_trimmed, family = gaussian(), prior = priors_nested,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model to evaluate main effects of case, number interference, sentence grammaticality, and their interactions in the post-critical region 
mrcadv1 <- brm(formula = log(rt) ~ case+int+gram+casexint+casexgram+intxgram+casexintxgram+
              (1+case+int+gram+casexint+casexgram+intxgram+casexintxgram|subj) + 
              (1+case+int+gram+casexint+casexgram+intxgram+casexintxgram|item),
            data = rcadv1_trimmed, family = gaussian(), prior = priors_three_way,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))

```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model to evaluate main effects of case, number interference, and their interaction in the post-critical region for the grammatical and ungrammatical sentences separately
mrcadv1_nested <- brm(formula = log(rt) ~ gram+case_g+int_g+casexint_g+case_u+int_u+casexint_u+
              (1+gram+case_g+int_g+casexint_g+case_u+int_u+casexint_u|subj) + 
              (1+gram+case_g+int_g+casexint_g+case_u+int_u+casexint_u|item),
            data = rcadv1_trimmed, family = gaussian(), prior = priors_nested,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))

```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model to evaluate the effect of number interference in the post-critical region for the grammatical sentences but in case match and case mismatch conditions separately
mrcadv1_nested_g <- brm(formula = log(rt) ~ case_g+attr_nom_g+attr_acc_g+
              (1+case_g+attr_nom_g+attr_acc_g|subj) + 
              (1+case_g+attr_nom_g+attr_acc_g|item),
            data = rcadv1_trimmed, family = gaussian(), prior = priors_nested_g,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

\newpage

# Reading time analysis results
In the tables below, each effect is described in terms of its posterior mean on log scale and the lower and upper bound of 95% credible interval.

## Critical region 
```{r}
# summarize model output in a table
kable(fixef(mrcv), 
      booktabs=T, 
      linesep = "",
      caption = "Analysis results for the reading times in the critical region showing estimates for the main effects case, number interference ('int'), grammaticality ('gram'), and their interactions.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case) - exp(b_Intercept - 
                                                       b_case))  %>%
  summarize(Estimate_case = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int) - exp(b_Intercept - 
                                                  b_int))  %>%
  summarize(Estimate_int = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))


#----------------------------------------------------#

posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_gram) - exp(b_Intercept - 
                                                  b_gram))  %>%
  summarize(Estimate_gram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexint) - exp(b_Intercept - 
                                                  b_casexint))  %>%
  summarize(Estimate_casexint = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexgram) - exp(b_Intercept - 
                                                  b_casexgram))  %>%
  summarize(Estimate_casexgram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#
posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_intxgram) - exp(b_Intercept - 
                                                  b_intxgram))  %>%
  summarize(Estimate_intxgram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexintxgram) - exp(b_Intercept - 
                                                  b_casexintxgram))  %>%
  summarize(Estimate_casexintxgram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

\newpage

```{r}
# summarize model output in a table
kable(fixef(mrcv_nested), 
      booktabs=T, 
      linesep = "",
      caption = "Analysis results for the reading times in the critical region showing estimates for the main effects of case, number interference ('int'), and their interaction within grammatical (x\\_g) and ungrammatical (x\\_u) sentences separately. Gram = grammaticality.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE)
```

***Model estimates back-transformed to milliseconds***
```{r}

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case_g) - exp(b_Intercept - 
                                                       b_case_g))  %>%
  summarize(Estimate_case_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_g) - exp(b_Intercept - 
                                                       b_int_g))  %>%
  summarize(Estimate_int_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexint_g) - exp(b_Intercept - 
                                                       b_casexint_g))  %>%
  summarize(Estimate_casexint_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case_u) - exp(b_Intercept - 
                                                       b_case_u))  %>%
  summarize(Estimate_case_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_u) - exp(b_Intercept - 
                                                       b_int_u))  %>%
  summarize(Estimate_int_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexint_u) - exp(b_Intercept - 
                                                       b_casexint_u))  %>%
  summarize(Estimate_casexint_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

## Post-critical region
```{r}
# summarize model output in a table
kable(fixef(mrcadv1), 
      booktabs=T, 
      linesep = "",
      caption = "Analysis results for the reading times in the post-critical region showing estimates for the main effects case, number interference ('int'), grammaticality ('gram'), and their interactions.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case) - exp(b_Intercept - 
                                                       b_case))  %>%
  summarize(Estimate_case = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int) - exp(b_Intercept - 
                                                  b_int))  %>%
  summarize(Estimate_int = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))


#----------------------------------------------------#

posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_gram) - exp(b_Intercept - 
                                                  b_gram))  %>%
  summarize(Estimate_gram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexint) - exp(b_Intercept - 
                                                  b_casexint))  %>%
  summarize(Estimate_casexint = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexgram) - exp(b_Intercept - 
                                                  b_casexgram))  %>%
  summarize(Estimate_casexgram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#
posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_intxgram) - exp(b_Intercept - 
                                                  b_intxgram))  %>%
  summarize(Estimate_intxgram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexintxgram) - exp(b_Intercept - 
                                                  b_casexintxgram))  %>%
  summarize(Estimate_casexintxgram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

```{r}
# summarize model output in a table
kable(fixef(mrcadv1_nested), 
      booktabs=T, 
      linesep = "",
      caption = "Analysis results for the reading times in the post-critical region showing estimates for the main effects of case, number interference ('int'), and their interaction within grammatical (x\\_g) and ungrammatical (x\\_u) sentences separately. Gram = grammaticality.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE)

```

***Model estimates back-transformed to milliseconds***
```{r}

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case_g) - exp(b_Intercept - 
                                                       b_case_g))  %>%
  summarize(Estimate_case_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_g) - exp(b_Intercept - 
                                                       b_int_g))  %>%
  summarize(Estimate_int_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexint_g) - exp(b_Intercept - 
                                                       b_casexint_g))  %>%
  summarize(Estimate_casexint_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case_u) - exp(b_Intercept - 
                                                       b_case_u))  %>%
  summarize(Estimate_case_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_u) - exp(b_Intercept - 
                                                       b_int_u))  %>%
  summarize(Estimate_int_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexint_u) - exp(b_Intercept - 
                                                       b_casexint_u))  %>%
  summarize(Estimate_casexint_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))
```

\newpage

```{r}
# summarize model output in a table
kable(fixef(mrcadv1_nested_g), 
      booktabs=T, 
      linesep = "",
      caption = "Analysis results showing estimates for the effect of number interference in the post-critical region for the grammatical sentences but in case match (nominative attractor; attr\\_nom\\_g) and case mismatch (accusative attractor; attr\\_acc\\_g) conditions separately.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE)

```

***Model estimates back-transformed to milliseconds***
```{r}

posterior_samples(mrcadv1_nested_g, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_attr_nom_g) - exp(b_Intercept - 
                                                       b_attr_nom_g))  %>%
  summarize(Estimate_interference_caseMatch = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#


posterior_samples(mrcadv1_nested_g, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_attr_acc_g) - exp(b_Intercept - 
                                                       b_attr_acc_g))  %>%
  summarize(Estimate_interference_caseMismatch = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

\newpage
# Plots
## By-region RTs for grammatical sentences
```{r}
targetRT_gram<-subset(targetTrimmed, cond %in% c("a", "b", "e", "f"))
targetRT_gram<-subset(targetRT_gram, pos %in% c("0", "1", "2", "3","4", "5"))

targetRT_gram %>%
  group_by(cond,pos) %>%
  summarize(
    mean.rt = mean(rt),
    se.lower = mean.rt - se(rt),
    se.upper = mean.rt + se(rt),
    ci.lower = mean.rt - 2*se(rt),
    ci.upper = mean.rt + 2*se(rt)) -> df_gram_byRegion

df_gram_byRegion$cond<-as.factor(df_gram_byRegion$cond)
df_gram_byRegion$pos<-factor(df_gram_byRegion$pos,levels=c("0","1","2",
                                     "3", "4","5"))

foo<-rep(0, nrow(df_gram_byRegion))
foo[with(df_gram_byRegion, pos == "0")] = 1
foo[with(df_gram_byRegion, pos == "1")] = 2
foo[with(df_gram_byRegion, pos == "2")] = 3
foo[with(df_gram_byRegion, pos == "3")] = 4
foo[with(df_gram_byRegion, pos == "4")] = 5
foo[with(df_gram_byRegion, pos == "5")] = 6

df_gram_byRegion$pos = with(df_gram_byRegion, reorder(pos, foo))
rm(foo)

## Change the factor level order
df_gram_byRegion$cond <- factor(df_gram_byRegion$cond, levels = c("b","a", "f","e"))

lbs=c("crit-3\nThe painter(s)","crit-2\nthat","crit-1\nthe sculptor","critical\nignored","crit+1\nexhibition", "crit+2\nduring")
pd <- position_dodge(.3)
p_gram_byRegion<-ggplot(df_gram_byRegion, aes(x=pos, y=mean.rt, group=cond, color=cond))+ 
  geom_errorbar(aes(ymin=se.lower, ymax=se.upper),
                width=.2, show.legend = FALSE, size=.4, position=pd)+
  geom_line(aes( color=cond, linetype=cond), position=pd,size=.4) +
  geom_point(aes(shape=cond, color=cond), size=2, position=pd)+
  scale_x_discrete(labels=lbs) +
  theme_bw(base_family = "sans", base_size = 12)+
  ylab("[ms]")+
  scale_color_manual(values = c("#0072B2", "#0072B2", "#082567", "#082567"),
                     labels = c("case match, no-interference",
                                "case match, interference",
                                "case mismatch, no-interference",
                                "case mismatch, interference"))+
  scale_shape_manual(values=c(16,16,15,15),
                    labels = c("case match, no-interference",
                                "case match, interference",
                                "case mismatch, no-interference",
                                "case mismatch, interference"))+
    scale_linetype_manual(values=c("solid", "dashed", "solid", "dashed"),
                   labels = c("case match, no-interference",
                                "case match, interference",
                                "case mismatch, no-interference",
                                "case mismatch, interference"))+
  theme(axis.text.x = element_text(
    face=c("plain","plain","plain","bold","bold","plain")),
    axis.title.x=element_blank(),
    legend.position = c(0.82,0.85), 
    legend.text = element_text(size=9),
    legend.key.width = unit(1.3,"cm"),
    legend.title=element_blank(),
    legend.key.size = unit(0.5, "cm"),
    legend.spacing.x = unit(0,"cm"),
    legend.margin=margin(t=-0.5, r=0, b=0, l=0, unit="cm")) 
```

```{r}
# Closeup look at RTs in critical and post-critical regions in grammatical sentences
targetRT_gram<-subset(targetRT_gram, pos %in% c("3","4"))

targetRT_gram %>%
  group_by(cond,pos) %>%
  dplyr::summarize(
    mean.rt = mean(rt),
    se.lower = mean.rt - se(rt),
    se.upper = mean.rt + se(rt),
    ci.lower = mean.rt - 2*se(rt),
    ci.upper = mean.rt + 2*se(rt)) -> df_gram

df_gram$Region<-ifelse(df_gram$pos 
                       %in% c("3"), "Critical region", "Critical+1 region")
df_gram$Interference <-ifelse(df_gram$cond 
                              %in% c("a","e"), "interference", "no-interference")
df_gram$Case <-ifelse(df_gram$cond 
                      %in% c("a","b"), "case match", "case mismatch")

## Change the factor level order
df_gram$Region <- factor(df_gram$Region, 
                         levels=c("Critical region", "Critical+1 region")) 
df_gram$Interference <- factor(df_gram$Interference, 
                               levels = c("no-interference","interference"))
df_gram$Case <- factor(df_gram$Case, 
                       levels = c("case match","case mismatch"))

pd <- position_dodge(.15)
lplot_gram<-ggplot(data =df_gram,
                   aes(x=Interference, y=mean.rt, group=Case, color=Case)) + 
    geom_errorbar(aes(ymin=se.lower, ymax=se.upper),
                  width=.1,size=.4, position=pd) +
  geom_line(linetype="solid", size=.4,position=pd) +
  geom_point(aes(shape=Case), size=2, show.legend = TRUE,position=pd) +
  scale_color_manual(values = alpha(c("#0072B2","#082567")))+
  scale_shape_manual(values=c(16,15)) +
  theme_bw(base_size = 12, base_family = "sans") +
  labs(y = "[ms]") +
  labs(shape="Condition",linetype="Condition",color="Condition") +
  theme(axis.title.x = element_blank(),
        legend.key.width = unit(1.3,"cm"),
        legend.position="top") 

lplot_gram + facet_grid(. ~  Region)+
  theme(strip.background = element_rect(fill="grey37"), # grey27
strip.text.x = element_text(face="bold", color="white", size =12)) ->lplot_gram
```

```{r fig.width=8, fig.height=8}
ggarrange(p_gram_byRegion, lplot_gram, nrow = 2, labels = c("A", "B"), font.label = list(size=14, family ="sans"), align="h")
                                              
ggsave("spr3_gram_byRegion.pdf", device = "pdf", width = 190, height = 190, units = "mm")
```

\newpage
## By-region RTs for ungrammatical sentences
```{r}
targetRT_ungram<-subset(targetTrimmed, cond %in% c("c", "d", "g", "h"))
targetRT_ungram<-subset(targetRT_ungram, pos %in% c("0", "1", "2", "3","4", "5"))

targetRT_ungram %>%
  group_by(cond,pos) %>%
  summarize(
    mean.rt = mean(rt),
    se.lower = mean.rt - se(rt),
    se.upper = mean.rt + se(rt),
    ci.lower = mean.rt - 2*se(rt),
    ci.upper = mean.rt + 2*se(rt)) -> df_ungram_byRegion

df_ungram_byRegion$cond<-as.factor(df_ungram_byRegion$cond)
df_ungram_byRegion$pos<-as.factor(df_ungram_byRegion$pos)
df_ungram_byRegion$pos<-factor(df_ungram_byRegion$pos,levels=c("0","1","2",
                                     "3", "4","5"))

foo<-rep(0, nrow(df_ungram_byRegion))
foo[with(df_ungram_byRegion, pos == "0")] = 1
foo[with(df_ungram_byRegion, pos == "1")] = 2
foo[with(df_ungram_byRegion, pos == "2")] = 3
foo[with(df_ungram_byRegion, pos == "3")] = 4
foo[with(df_ungram_byRegion, pos == "4")] = 5
foo[with(df_ungram_byRegion, pos == "5")] = 6

df_ungram_byRegion$pos = with(df_ungram_byRegion, reorder(pos, foo))
rm(foo)

lbs=c("crit-3\nThe painter(s)","crit-2\nthat","crit-1\nthe sculptor","critical\nignored","crit+1\nexhibition", "crit+2\nduring")
pd <- position_dodge(.3)
p_ungram_byRegion<-ggplot(df_ungram_byRegion, aes(x=pos, y=mean.rt, group=cond, color=cond))+ 
  geom_errorbar(aes(ymin=se.lower, ymax=se.upper),
                width=.2, show.legend = FALSE, size=.4,position=pd)+
  geom_line(aes( color=cond, linetype=cond), position=pd,size=.4) +
  geom_point(aes(shape=cond, color=cond), size=2, position=pd)+
  scale_x_discrete(labels=lbs) +
  theme_bw(base_family = "sans", base_size = 12)+
  ylab("[ms]")+
  scale_color_manual(values = c("red3", "red3", "#660000", "#660000"), 
                     labels = c("case match, no-interference",
                                "case match, interference",
                                "case mismatch, no-interference",
                                "case mismatch, interference"))+
  scale_shape_manual(values=c(17,17,15,15),
                    labels = c("case match, no-interference",
                                "case match, interference",
                                "case mismatch, no-interference",
                                "case mismatch, interference"))+
    scale_linetype_manual(values=c("solid", "dashed", "solid", "dashed"),
                   labels = c("case match, no-interference",
                                "case match, interference",
                                "case mismatch, no-interference",
                                "case mismatch, interference"))+
  theme(axis.text.x = element_text(
    face=c("plain","plain","plain","bold","bold","plain")),
        axis.title.x=element_blank(),
        legend.position = c(0.82,0.85),
        legend.key.width = unit(1.3,"cm"),
        legend.title=element_blank(),
        legend.key.size = unit(0.5, "cm"), # space between keys
        legend.text = element_text(size=9),
        legend.spacing.x = unit(0,"cm"),
        legend.margin = margin(t=-0.5, r=0, b=0, l=0, unit="cm")) 
```

```{r}
# Closeup look at RTs in critical and post-critical regions in ungrammatical sentences
targetRT_ungram<-subset(targetRT_ungram, pos %in% c("3","4"))

targetRT_ungram %>%
  group_by(cond,pos) %>%
  summarize(
    mean.rt = mean(rt),
    se.lower = mean.rt - se(rt),
    se.upper = mean.rt + se(rt),
    ci.lower = mean.rt - 2*se(rt),
    ci.upper = mean.rt + 2*se(rt)) -> df_ungram

df_ungram$Region<-ifelse(df_gram$pos 
                         %in% c("3"), "Critical region", "Critical+1 region")
df_ungram$Interference <-ifelse(df_ungram$cond 
                                %in% c("d","h"), "interference", "no-interference")
df_ungram$Case <-ifelse(df_ungram$cond 
                        %in% c("c","d"), "case match", "case mismatch")

## Change the factor level order
df_ungram$Region <- factor(df_ungram$Region, 
                           levels=c("Critical region", "Critical+1 region")) 
df_ungram$Interference <- factor(df_ungram$Interference, 
                                 levels = c("no-interference","interference"))
df_ungram$Case <- factor(df_ungram$Case, 
                         levels = c("case match","case mismatch"))

pd <- position_dodge(.15)
lplot_ungram<-ggplot(data =df_ungram,
                     aes(x=Interference, y=mean.rt, group=Case, color=Case)) + 
    geom_errorbar(aes(ymin=se.lower, ymax=se.upper),
                  width=.1, size=.4, position=pd) +
  geom_line(linetype="solid", size=.4,position=pd) +
  geom_point(aes(shape=Case), size=2, show.legend = TRUE,position=pd) +
  scale_color_manual(values = alpha(c("red3", "#660000"))) +
  scale_shape_manual(values=c(17,15)) +
  theme_bw(base_size = 12, base_family = "sans") +
  labs(y = "[ms]") +
  labs(shape="Condition",linetype="Condition",color="Condition") +
  theme(axis.title.x = element_blank(),
        legend.key.width = unit(1.3,"cm"),
        legend.position="top") 

lplot_ungram + facet_grid(. ~  Region)+
  theme(strip.background = element_rect(fill="grey37"),
strip.text.x = element_text(size=12, face="bold", color="white")) ->lplot_ungram

```

```{r fig.width=8, fig.height=8}
ggarrange(p_ungram_byRegion, lplot_ungram, nrow = 2, labels = c("A", "B"), font.label = list(size=14, family ="sans"))

ggsave("spr3_ungram_byRegion.pdf", device = "pdf", width = 190, height = 190, units = "mm")
```

## Density plots
```{r}
# Plot posterior probability distributions of the main effects of grammaticality, interference, case, and their interactions in the critical region
df1 <- posterior_samples(mrcv, pars= c("b") ) %>%
  mutate(gram_effect = exp(b_Intercept + b_gram) - exp(b_Intercept - b_gram),
         int_effect = exp(b_Intercept + b_int) - exp(b_Intercept - b_int),
         case_effect = exp(b_Intercept + b_case) - exp(b_Intercept - b_case),
         intGram_effect = exp(b_Intercept + b_intxgram) - exp(b_Intercept - b_intxgram),
         caseGram_effect = exp(b_Intercept + b_casexgram) - exp(b_Intercept - b_casexgram),
         caseInt_effect = exp(b_Intercept + b_casexint) - exp(b_Intercept - b_casexint),
         caseIntGram_effect = exp(b_Intercept + b_casexintxgram) - exp(b_Intercept - b_casexintxgram))
 

color_scheme_set("gray")
bayesplot_theme_set(theme_default(base_size = 12, base_family = "sans")) 
rcv_densityPlot<-mcmc_areas(
 df1,
  pars = c("caseIntGram_effect","caseInt_effect","caseGram_effect","intGram_effect","case_effect",
           "int_effect","gram_effect"),
  prob = 0.95, # 80% intervals
  prob_outer = 0.99, 
  point_est = "mean"
) +
  ggplot2::scale_y_discrete(
    labels = c("case × interference \n × grammaticality",
               "case × \n interference",
               "case × \n grammaticality",
               "interference × \n grammaticality", 
               "case", "interference", "grammaticality")) +
  geom_vline(
    xintercept=0, linetype="dashed", 
    color="red", size=.5) +
  labs(title = "Main effects and interactions",
       subtitle = "Critical region") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))
```

```{r}
# Plot posterior probability distributions of the main effects of number interference, case, and their interaction in the critical region for the grammatical sentences 
df2<-posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(attr_effect = exp(b_Intercept + b_int_g) - exp(b_Intercept - b_int_g),
         case_effect = exp(b_Intercept + b_case_g) - exp(b_Intercept - b_case_g),
         inter_effect = exp(b_Intercept + b_casexint_g) - exp(b_Intercept - b_casexint_g))
 
color_scheme_set("gray")
rcv_nestedG_densityPlot<-mcmc_areas(
 df2,
  pars = c("inter_effect","case_effect","attr_effect"),
  prob = 0.95, 
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(
    labels = c("case × \n interference",
               "case","interference")) +
  geom_vline(xintercept=0, linetype="dashed", 
             color="red", size=.5) +
  labs(x = "Estimates [ms]", 
       title = "Nested comparisons",
       subtitle = "Critical region: grammatical items") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))
```

```{r}
# Plot posterior probability distributions of the main effects of number interference, case, and their interaction in the critical region for the ungrammatical sentences
df3 <- posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(attr_effect = exp(b_Intercept + b_int_u) - exp(b_Intercept - b_int_u),
         case_effect = exp(b_Intercept + b_case_u) - exp(b_Intercept - b_case_u),
         inter_effect = exp(b_Intercept + b_casexint_u) - exp(b_Intercept - b_casexint_u))
 
color_scheme_set("gray")
rcv_nestedU_densityPlot<-mcmc_areas(
 df3,
  pars = c("inter_effect","case_effect","attr_effect"),
  prob = 0.95, 
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(
    labels = c("case × \ninterference","case","interference")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(x = "Estimates [ms]", 
       title = "Nested comparisons",
       subtitle = "Critical region: ungrammatical items") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))

```

```{r}

spr3_Crit_Density <- ggarrange(rcv_densityPlot,                                                 # First row with scatter plot
          ggarrange(rcv_nestedG_densityPlot + 
                                    theme(axis.title.x = element_blank()), 
                    rcv_nestedU_densityPlot + 
                                    theme(axis.text.y = element_blank(),
                                    axis.ticks.y = element_blank(),
                                    axis.title.x = element_blank()), 
                    ncol = 2, labels = c("B", "C"), align = "hv", 
                    font.label = list(size=14, family ="sans")), 
          nrow = 2, 
          labels = "A" ,                                      
          font.label = list(size=14, family ="sans")) 
```

```{r fig.width=8, fig.height=8}
annotate_figure(spr3_Crit_Density,
                bottom = text_grob("Estimates [ms]", 
                                   size = 12, 
                                   family="sans"))
 
ggsave("spr3_Crit_Density.pdf", device = "pdf", width = 190, height = 190, units = "mm")
```

```{r}
# Plot posterior probability distributions of the main effects of grammaticality, interference, case, and their interactions in the post-critical region
df4<-posterior_samples(mrcadv1, pars= c("b") ) %>%
  mutate(gram_effect = exp(b_Intercept + b_gram) - exp(b_Intercept - b_gram),
         int_effect = exp(b_Intercept + b_int) - exp(b_Intercept - b_int),
         case_effect = exp(b_Intercept + b_case) - exp(b_Intercept - b_case),
         intGram_effect = exp(b_Intercept + b_intxgram) - exp(b_Intercept - b_intxgram),
         caseGram_effect = exp(b_Intercept + b_casexgram) - exp(b_Intercept - b_casexgram),
         caseInt_effect = exp(b_Intercept + b_casexint) - exp(b_Intercept - b_casexint),
         caseIntGram_effect = exp(b_Intercept + b_casexintxgram) - exp(b_Intercept - b_casexintxgram))
 

color_scheme_set("gray")
rcadv1_densityPlot<-mcmc_areas(
 df4,
  pars = c("caseIntGram_effect",
           "caseInt_effect",
           "caseGram_effect",
           "intGram_effect",
           "case_effect",
           "int_effect",
           "gram_effect"),
  prob = 0.95, 
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(
    labels = c("case × interference \n × grammaticality",
               "case × \n interference",
               "case × \n grammaticality",
               "interference × \n grammaticality", 
               "case", "interference", "grammaticality")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
 labs(title = "Main effects and interactions",
      subtitle = "Post-critical region") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))

```

```{r}
# Plot posterior probability distributions of the main effects of number interference, case, and their interaction in the post-critical region for the grammatical sentences 
df5<-posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(attr_effect = exp(b_Intercept + b_int_g) - exp(b_Intercept - b_int_g),
         case_effect = exp(b_Intercept + b_case_g) - exp(b_Intercept - b_case_g),
         inter_effect = exp(b_Intercept + b_casexint_g) - exp(b_Intercept - b_casexint_g))
 
color_scheme_set("gray")
rcadv1_nestedG_densityPlot<-mcmc_areas(
 df5,
  pars = c("inter_effect","case_effect","attr_effect"),
  prob = 0.95, 
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(
    labels = c("case × \n interference","case","interference")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs( x = "Estimates [ms]", 
       title = "Nested comparisons",
       subtitle = "Post-critical region: grammatical items") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"),
        plot.subtitle = element_text(size = 11))
```

```{r}
# Plot posterior probability distributions of the main effects of number interference, case, and their interaction in the postcritical region for the ungrammatical sentences 
df6<-posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(attr_effect = exp(b_Intercept + b_int_u) - exp(b_Intercept - b_int_u),
         case_effect = exp(b_Intercept + b_case_u) - exp(b_Intercept - b_case_u),
         inter_effect = exp(b_Intercept + b_casexint_u) - exp(b_Intercept - b_casexint_u))
 
color_scheme_set("gray")
rcadv1_nestedU_densityPlot<-mcmc_areas(
 df6,
  pars = c("inter_effect","case_effect","attr_effect"),
  prob = 0.95, 
  prob_outer = 0.99, 
  point_est = "mean") +
   ggplot2::scale_y_discrete(
     labels = c("case × \n interference","case","interference")) +
 geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(x = "Estimates [ms]", 
       title = "Nested comparisons",
       subtitle = "Post-critical region: ungrammatical items") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"),
       plot.subtitle = element_text(size = 11))
```

```{r}

spr3_postCrit_Density <- ggarrange(rcadv1_densityPlot,                                                 # First row with scatter plot
          ggarrange(rcadv1_nestedG_densityPlot + 
                                    theme(axis.title.x = element_blank()), 
                    rcadv1_nestedU_densityPlot + 
                                    theme(axis.text.y = element_blank(),
                                    axis.ticks.y = element_blank(),
                                    axis.title.x = element_blank()), 
                    ncol = 2, labels = c("B", "C"), align = "hv", 
                    font.label = list(size=14, family ="sans")), 
          nrow = 2, 
          labels = "A" ,                                      
          font.label = list(size=14, family ="sans")) 


```

```{r fig.width=8, fig.height=8}
annotate_figure(spr3_postCrit_Density,
                bottom = text_grob("Estimates [ms]", 
                                   size = 12, 
                                   family="sans"))

ggsave("spr3_postCrit_Density.pdf", device = "pdf", width = 190, height = 190, units = "mm")

```