---
title: "Experiment 2 (self-paced reading)"
output: pdf_document
---

\large{R code to reproduce the analysis of Experiment 2 reported in the manuscript \emph{"Does case marking affect agreement attraction in comprehension?"}.} 

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.path='figures/fig-',
               fig.align='center',
               fig.show='hold',warning=FALSE,message=FALSE, echo = FALSE)

```

```{r load_data}
# Load packages
library(dplyr)
library(knitr)
library(kableExtra)
library(brms)
library(MASS)
library(ggplot2)
library(binom)
library(boot) # for backtransformations
library(ggpubr)
library(brmstools)
library(rstanarm)
library(bayesplot)

# Define functions
# Function to calculate standard error.
se <- function(x) {
    return(sqrt(var(x,na.rm=TRUE)/length(na.omit(x))))
}

# Function to calculate binomial standard error.
se.bin <- function(x){
  n.success = sum(na.omit(x)) #x is coded as 1 (success) or 0 (failure), so number of successes is the sum of x = 1 
  n         = length(na.omit(x))
  p         = n.success / n
  return(sqrt(p*(1-p)/n))
}

# Load data
d <- read.csv("E2_data.csv", encoding="UTF-8", header=T)
```

# Participants 
```{r}
# Summarize demographic data in a table
demographic <- d[!duplicated(d$subj),] # leave one row per participant
demographicRel <- demographic[9:14] # select columns with relevant info

options(knitr.kable.NA = '') # exclude NAs in the table
kable(summary(demographicRel), 
      booktabs=T, 
      caption="Summary of participants' demographic characteristics. Data from all 48 participants were included in the analysis.")  %>%
  kable_styling(latex_options = c("basic", "scale_down", "hold_position")) %>% 
  row_spec(0,bold=TRUE)

```

```{r subset_data}
# Subset data and convert factors
d$subj<-factor(d$subj,levels=unique((d$subj))) 
d<-subset(d,expt!="practice") # remove practice items

filler<-subset(d, expt=="filler" & pos=="?") # subset filler items
filler$expt<-factor(filler$expt,levels="filler")
filler$accuracy<-as.numeric(as.character(filler$accuracy)) 

target<-subset(d, expt=="attraction") # subset experimental items
target$cond<-factor(target$cond,levels=letters[1:4]) 
target$expt<-factor(target$expt,levels="attraction")
```

```{r data_summary, eval=FALSE}
summary(d[,-6]) # exclude the column w/Armenian characters to prevent execution error
```

# Contrast coding 
Note that the term “interference” applies to sentences with singular attractors in
grammatical sentences (i.e., "a") but plural attractors in ungrammatical sentences (i.e., "d").

***Main effects and interaction***
```{r echo=TRUE}
# Contrasts to evaluate the main effects of grammaticality ('gram'), 
# number interference ('int'), and their interaction
##         a   b    c   d
#gram      1   1   -1  -1 # grammatical is 1, ungrammaticals is -1
#int       1  -1   -1   1 # No-interference is -1, interference is 1
target$gram<-ifelse(target$cond%in%c("a","b"),1,-1)
target$int<-ifelse(target$cond%in%c("a","d"),1,-1)
target$gramxint<-target$gram*target$int
```

***Nested comparisons***
```{r echo=TRUE}
# Contrasts to evaluate the number interference effect in grammatical (int_g)
# and ungrammatical (int_u) sentences separately
##          a   b   c   d
#gram       1   1  -1  -1 # grammatical is 1, ungrammaticals is -1
#int_g      1  -1   0   0 # No-interference is -1, interference is 1
#int_u      0   0  -1   1
target$int_g <-ifelse(target$cond=="a",1,ifelse(target$cond=="b",-1,0))
target$int_u <-ifelse(target$cond=="c",-1,ifelse(target$cond=="d",1,0))
```

\newpage

# Filler accuracy 
* Overall accuracy (%) for the filler items
```{r}
filler %>% dplyr::summarize(
  fillerAccuracy = round(100*mean(accuracy, na.rm = TRUE), digits=1),
  fillerSE = round(100*se.bin(accuracy), digits=1)) 
```

\vspace{0.5cm}

```{r fig.height=4, fig.width=7}
# Compute mean accuracy for each participant for the filler items
fillerAcc_bySubj <- filler %>% group_by(subj) %>% summarize(Filler_accuracy = round(100 *mean(accuracy), digits = 0))

fillerAcc_bySubj$subj<-as.numeric(as.character
                                  (fillerAcc_bySubj$subj))

# Plot mean accuracy for each participant for the filler items  
ggplot(fillerAcc_bySubj, aes(x = subj, y = Filler_accuracy )) + 
  geom_point() +
  scale_x_continuous(name="Participants", breaks=seq(1,48,2)) +
  ylab("Accuracy (%)") -> bySubj_fillerPlot

# Add titles
bySubj_fillerPlot + labs(
  title = "Mean accuracy per participant for the filler items",
  subtitle = "Accuracy ranges from 71% to 100%")

#range(fillerAcc_bySubj$Filler_accuracy)
```

\newpage

# Target accuracy
* Overall accuracy (%) for the experimental items
```{r}
targetAcc<-subset(target,  pos=="?")
targetAcc$accuracy<-as.numeric(as.character(targetAcc$accuracy))

# Compute overall target accuracy
targetAcc %>% dplyr::summarize(
  trgAccuracy = round(100*mean(accuracy, na.rm = TRUE), digits=1),
  trgSE = round(100*se.bin(accuracy), digits=1))
```

```{r eval=FALSE}
# Sanity check: everything is balanced
xtabs(~subj+cond,targetAcc)
xtabs(~item+cond,targetAcc)
xtabs(~subj+item,targetAcc)
```

\vspace{0.5cm}

```{r}
# Compute mean accuracy for each condition for the experimental items
target_acc_byCond <-targetAcc %>% group_by(cond) %>% summarize(
  trgAccuracy = round(100 *mean(accuracy), digits = 1),
  trgSE =  round(100*se.bin(accuracy), digits=1))

colnames(target_acc_byCond) <- c("Condition", "Accuracy [%]", "SE")
target_acc_byCond <- as.data.frame(target_acc_byCond)
rownames(target_acc_byCond) <- c("grammatical, interference (w/sg. attractor)",
                                 "grammatical, no-interference (w/pl. attractor)",
                                 "ungrammatical, no-interference (w/sg. attractor)",
                                 "ungrammatical, interference (w/pl. attractor)")

# Present mean accuracy for each condition in a table
target_acc_byCond %>%
  kable(align="c", booktabs = T, 
        caption = "Mean accuracy per condition for the experimental items") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "22em")
```

\vspace{0.5cm}

```{r}
# Compute mean accuracy for each participant for the experimental items
targetAcc_bySubj <- targetAcc %>% group_by(subj) %>% summarize(target_accuracy = round(100 *mean(accuracy), digits = 0))

targetAcc_bySubj$subj<-as.numeric(as.character
                                  (targetAcc_bySubj$subj))


# Plot mean accuracy for each participant for the experimental items
ggplot(targetAcc_bySubj, aes(x = subj, y = target_accuracy )) + 
  geom_point() +
  scale_x_continuous(name="Participants", breaks=seq(1,48,2)) +
  ylab("Accuracy (%)") -> bySubj_targetPlot

# Add titles
bySubj_targetPlot + labs(
  title = "Mean accuracy per participant for the experimental items",
  subtitle = "Accuracy ranges from 67% to 100%")

# range(targetAcc_bySubj$target_accuracy)
```
\newpage

# Reading time data 
```{r}
# Pre-process RT data/subset
targetRT<-subset(target,pos!="?")
colnames(targetRT)[7]<-"region"
colnames(targetRT)[6]<-"word"

targetRT$region<-factor(targetRT$region)

rcverb<-subset(targetRT,region=="rcv") # subset RT in the critical region
rcadv1<-subset(targetRT, region=="rcadv1") # subset RT in the post-critical region
```

***RT trimming.*** RTs below 200ms and above 8000ms are excluded.
```{r echo=TRUE}
## percent of data points trimmed across all regions
targetTrimmed<-subset(targetRT, rt>200 & rt<8000)
round(100*((dim(targetRT)[1]-dim(targetTrimmed)[1])/dim(targetRT)[1]), digits=1)

## percent of data points trimmed in the critical region 
rcverb_trimmed<-subset(rcverb, rt>200 & rt<8000)
round(100*((dim(rcverb)[1]-dim(rcverb_trimmed)[1])/dim(rcverb)[1]), digits=2)

## percent of data points trimmed in the post-critical region 
rcadv1_trimmed<-subset(rcadv1, rt>200 & rt<8000)
round(100*((dim(rcadv1)[1]-dim(rcadv1_trimmed)[1])/dim(rcadv1)[1]), digits=2)
```

\vspace{0.5cm}

```{r}
# Create RT boxplots for critical region
op<-par(mfrow=c(1,2) ,pty="m")

boxplot(rt~cond,rcverb_trimmed, 
        col=c("grey","black"), 
        border="brown", 
        notch=TRUE, 
        main="Raw RTs in critical region")

boxplot(log(rt)~cond,rcverb_trimmed, 
        col=c("grey","black"), 
        border="brown", 
        notch=TRUE, 
        main="Log RTs in critical region")

```

```{r}
# Create RT boxplots for post-critical region
op<-par(mfrow=c(1,2) ,pty="m")
boxplot(rt~cond,rcadv1_trimmed, 
        col=c("grey","black"), 
        border="brown", 
        notch=TRUE, 
        main="Raw RTs in post-critical region")

boxplot(log(rt)~cond,rcadv1_trimmed, 
        col=c("grey","black"), 
        border="brown", 
        notch=TRUE, 
        main="Log RTs in post-critical region")
```

```{r eval=FALSE}
# Create RT boxplots for critical+2 region
op<-par(mfrow=c(1,2) ,pty="m")

boxplot(rt~cond,rcadv2_trimmed, 
        col=c("grey","black"), 
        border="brown", notch=TRUE, 
        main="Raw RTs in critical+2 region")

boxplot(log(rt)~cond,rcadv2_trimmed, 
        col=c("grey","black"), 
        border="brown", notch=TRUE, 
        main="Log RTs in critical+2 region")
```

```{r}
# Compute mean RTs in the critical region for the four conditions
critRT_byCond <- rcverb_trimmed %>% 
  group_by(cond) %>% 
  summarize(
  rtMean = round(mean(rt), digits = 0),
  rtSE = round(se(rt), digits = 0)
  )

colnames(critRT_byCond) <- c("Condition", "Mean RT [ms]", "SE")
critRT_byCond <- as.data.frame(critRT_byCond)
rownames(critRT_byCond) <- c("grammatical, interference (w/sg. attractor)",
                                 "grammatical, no-interference (w/pl. attractor)",
                                 "ungrammatical, no-interference (w/sg. attractor)",
                                 "ungrammatical, interference (w/pl. attractor)")

# Present mean RTs in the critical region in a table
critRT_byCond %>%
  kable(align="c", booktabs = T, 
        caption = "Mean reading times in the critical region for the four conditions") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "22em")

```

\vspace{0.5cm}

```{r}
# Compute mean RTs in the post-critical region for the four conditions
postCritRT_byCond<-rcadv1_trimmed %>% group_by(cond) %>% summarize(
  rtMean = round(mean(rt), digits = 0),
  rtSE = round(se(rt), digits = 0))

colnames(postCritRT_byCond) <- c("Condition", "Mean RT [ms]", "SE")
postCritRT_byCond <- as.data.frame(postCritRT_byCond)
rownames(postCritRT_byCond) <- c("grammatical, interference (w/sg. attractor)",
                                 "grammatical, no-interference (w/pl. attractor)",
                                 "ungrammatical, no-interference (w/sg. attractor)",
                                 "ungrammatical, interference (w/pl. attractor)")

# Present mean RTs in the post-critical region in a table
postCritRT_byCond %>%
  kable(align="c", booktabs = T, 
        caption = "Mean reading times in the post-critical region for the four conditions") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "22em")
```

\newpage

# Priors 
```{r echo=TRUE}
# Priors for reading time analysis involving main effects and interaction
priors_two_way <- c(set_prior("normal(0,10)", class="Intercept"),
                 set_prior("normal(0,1)", class="b", coef="gram"),
                 set_prior("normal(0,1)", class="b", coef="int"),
                 set_prior("normal(0,1)", class="b", coef="gramxint"),
                 set_prior("normal(0,1)", class="sd"),
                 set_prior("normal(0,1)", class="sigma"),
                 set_prior("lkj(2)", class="cor"))
```

```{r echo=TRUE}
# Priors for reading time analysis involving nested comparisons
priors_nested<- c(set_prior("normal(0,10)", class="Intercept"),
           set_prior("normal(0,1)", class="b", coef="gram"),
           set_prior("normal(0,1)", class="b", coef="int_g"),
           set_prior("normal(0,1)", class="b", coef="int_u"),
           set_prior("normal(0,1)", class="sd"),
           set_prior("normal(0,1)", class="sigma"),
           set_prior("lkj(2)", class="cor"))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for RTs in the critical region to evaluate main effects of sentence grammaticality, number interference, and their interaction
mrcv_int <- brm(formula = log(rt) ~ gram+int+gramxint+
              (1+gram+int+gramxint|subj) + 
              (1+gram+int+gramxint|item),
            data = rcverb_trimmed, family = gaussian(), prior = priors_two_way,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for RTs in the critical region to evaluate number interference effect in grammatical and ungrammatical sentences separately 
mrcv_nested <- brm(formula = log(rt) ~ gram+int_g+int_u+
              (1+gram+int_g+int_u|subj) + 
              (1+gram+int_g+int_u|item),
            data = rcverb_trimmed, family = gaussian(), prior = priors_nested,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for RTs in the post-critical region to evaluate main effects of sentence grammaticality, number interference, and their interaction
mrcadv1_int <- brm(formula = log(rt) ~ gram+int+gramxint+
              (1+gram+int+gramxint|subj) + 
              (1+gram+int+gramxint|item),
            data = rcadv1_trimmed, family = gaussian(), prior = priors_two_way,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for RTs in the post-critical region to evaluate number interference effect in grammatical and ungrammatical sentences separately
mrcadv1_nested <- brm(formula = log(rt) ~ gram+int_g+int_u+
              (1+gram+int_g+int_u|subj) + 
              (1+gram+int_g+int_u|item),
            data = rcadv1_trimmed, family = gaussian(), prior = priors_nested,
            iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

\newpage

# Reading time analysis results
In the tables below, each effect is described in terms of its posterior mean on log scale and the lower and upper bound of 95% credible interval.

## Critical region
```{r}
# summarize model output in a table
kable(fixef(mrcv_int), 
      booktabs=T, 
      caption = "Analysis results for the reading times in the critical region showing estimates for the main effects of grammaticality ('gram') and number interference ('int') as well as their interaction.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrcv_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_gram) - exp(b_Intercept - 
                                                       b_gram))  %>%
  summarize(Estimate_gram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int) - exp(b_Intercept - 
                                                       b_int))  %>%
  summarize(Estimate_int = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_gramxint) - exp(b_Intercept - 
                                                       b_gramxint))  %>%
  summarize(Estimate_gramxint = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

```{r}
# summarize model output in a table
kable(fixef(mrcv_nested), 
      booktabs=T, 
      caption = "Analysis results for the reading times in the critical region showing estimates for the number interference effect in the grammatical (int\\_g) and ungrammatical sentences (int\\_u) separately.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_g) - exp(b_Intercept - 
                                                       b_int_g))  %>%
  summarize(Estimate_int_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_u) - exp(b_Intercept - 
                                                       b_int_u))  %>%
  summarize(Estimate_int_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

\newpage

## Post-critical region
```{r}
# summarize model output in a table
kable(fixef(mrcadv1_int), 
      booktabs=T, 
      caption = "Analysis results for the reading times in the post-critical region showing estimates for the main effects of grammaticality ('gram') and number interference ('int') as well as their interaction.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE)
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrcadv1_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_gram) - exp(b_Intercept - 
                                                       b_gram))  %>%
  summarize(Estimate_gram = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int) - exp(b_Intercept - 
                                                       b_int))  %>%
  summarize(Estimate_int = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_gramxint) - exp(b_Intercept - 
                                                       b_gramxint))  %>%
  summarize(Estimate_gramxint = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

```{r}
# summarize model output in a table
kable(fixef(mrcadv1_nested), 
      booktabs=T, 
      caption = "Analysis results for the reading times in the post-critical region showing estimates for the number interference effect in the grammatical (int\\_g) and ungrammatical sentences (int\\_u) separately.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_g) - exp(b_Intercept - 
                                                       b_int_g))  %>%
  summarize(Estimate_int_grammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_int_u) - exp(b_Intercept - 
                                                       b_int_u))  %>%
  summarize(Estimate_int_ungrammatical = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```


# Plots
## By-region RT plot
```{r}
# Plot region-by-region reading times
dataPlots <- subset(
  targetTrimmed, region %in% c("mcsubj", "rcpron", "rcsubj", "rcv", "rcadv1", "rcadv2"))

dataPlots %>%
  group_by(cond,region) %>%
  summarize(
    mean.rt = mean(rt),
    se.lower = mean.rt - se(rt),
    se.upper = mean.rt + se(rt),
    ci.lower = mean.rt - 2*se(rt),
    ci.upper = mean.rt + 2*se(rt)) -> df_byRegion

df_byRegion$cond<-as.factor(df_byRegion$cond)
df_byRegion$region<-factor(df_byRegion$region,levels=c("mcsubj","rcpron","rcsubj",
                                     "rcv", "rcadv1","rcadv2"))

foo<-rep(0, nrow(df_byRegion))
foo[with(df_byRegion, region == "mcsubj")] = 1
foo[with(df_byRegion, region == "rcpron")] = 2
foo[with(df_byRegion, region == "rcsubj")] = 3
foo[with(df_byRegion, region == "rcv")] =    4
foo[with(df_byRegion, region == "rcadv1")] = 5
foo[with(df_byRegion, region == "rcadv2")] = 6

df_byRegion$region = with(df_byRegion, reorder(region, foo))
rm(foo)

## Change the factor level order
df_byRegion$cond <- factor(df_byRegion$cond, levels = c("b","a", "c","d"))

lbs=c("crit-3\nThe painter(s)","crit-2\nthat","crit-1\nthe sculptor","critical\nignored","crit+1\nexhibition", "crit+2\nduring")
pd <- position_dodge(.3)
p_byRegion <- ggplot(df_byRegion, 
                     aes(x=region, y=mean.rt, group=cond, color = cond))+ 
  geom_errorbar(aes(ymin=se.lower, ymax=se.upper),
                width=.2,size=.4,show.legend = FALSE, position=pd) +
  geom_line(aes(color=cond, linetype=cond), position=pd, size=.4) +
  geom_point(aes(shape=cond, color=cond), size = 2, position=pd) +
  scale_x_discrete(labels=lbs) +
  theme_bw(base_family = "sans", base_size = 12)+
  ylab("[ms]")+
  scale_color_manual(values = c("#0072B2", "#0072B2", "red3", "red3"),
                     labels = c("grammatical, no-interference",
                                "grammatical, interference",
                                "ungrammatical, no-interference",
                                "ungrammatical, interference"))+
  scale_linetype_manual(values=c("solid", "dashed", "solid", "dashed"),
                   labels = c("grammatical, no-interference",
                                "grammatical, interference",
                                "ungrammatical, no-interference",
                                "ungrammatical, interference"))+
  scale_shape_manual(values=c(16,16, 17, 17),
                     labels = c("grammatical, no-interference",
                                "grammatical, interference",
                                "ungrammatical, no-interference",
                                "ungrammatical, interference"))+
  theme(axis.text.x = element_text(
        face=c("plain","plain","plain","bold","bold","plain")),
        axis.title.x=element_blank(),
        legend.position = c(0.82,0.85),
        legend.key.width = unit(1.3,"cm"),
        legend.title=element_blank(),
        legend.key.size = unit(0.5, "cm"),
        legend.text = element_text(size=9),
        legend.spacing.x = unit(0,"cm"),
        legend.margin = margin(t=-0.5, r=0, b=0, l=0, unit="cm"))
```

```{r}
# Closeup plots of RTs in critical and post-critical regions
rtCritRegions <- subset(dataPlots, 
                               region %in% c("rcv","rcadv1"))

rtCritRegions %>%
  group_by(cond,region) %>%
  dplyr::summarize(
    mean.rt = mean(rt),
    se.lower = mean.rt - se(rt),
    se.upper = mean.rt + se(rt),
    ci.lower = mean.rt - 2*se(rt),
    ci.upper = mean.rt + 2*se(rt)) -> df_critReg

df_critReg$Region <- ifelse(df_critReg$region 
                            %in% c("rcv"), "Critical region", "Critical+1 region")
df_critReg$Interference <- ifelse(df_critReg$cond 
                                  %in% c("a","d"), "interference", "no-interference")
df_critReg$Grammaticality <- ifelse(df_critReg$cond 
                                    %in% c("a","b"), "grammatical", "ungrammatical")

## Change the factor level order
df_critReg$Region <- factor(df_critReg$Region,
                            levels=c("Critical region", "Critical+1 region")) 
df_critReg$Interference <- factor(df_critReg$Interference,
                                  levels = c("no-interference","interference"))
df_critReg$Grammaticality <- factor(df_critReg$Grammaticality,
                                    levels = c("grammatical","ungrammatical"))

pd <- position_dodge(.15)

lplot_critReg<-ggplot(
  data =df_critReg,
  aes(x=Interference, y=mean.rt, group=Grammaticality, color=Grammaticality)) +
  geom_errorbar(
    aes(ymin=se.lower, ymax=se.upper),
    width=.1,size=.4, position=pd) +
  geom_line(linetype="solid", size=.4, position=pd) +
  geom_point(aes(shape=Grammaticality, color=Grammaticality), 
             size=2, show.legend = TRUE, position=pd) +
  scale_color_manual(values = c("#0072B2","red3")) +
  scale_shape_manual(values=c(16,17)) +
  theme_bw(base_size = 12, base_family = "sans") +
  labs(y = "[ms]")+
  labs(shape="Condition",linetype="Condition",color="Condition") +
  theme(axis.title.x = element_blank(),
        legend.key.width = unit(1.3,"cm"),
        legend.position="top") 

lplot_critReg + facet_grid(. ~  Region) +
  theme(strip.background = element_rect(fill="grey37"),
        strip.text.x = element_text(size=12, face="bold", color="white")) -> lplot_critReg

```

```{r fig.height=7}
ggarrange(p_byRegion,lplot_critReg, nrow = 2, labels = c("A", "B"), 
          font.label = list(size=14, family ="sans"), align="h")
                                              
ggsave("spr1_byRegion.pdf", device = "pdf", width = 190, height = 190, units = "mm")
```

## Density plots
```{r}
# Posterior probability distributions of main effects and interaction in the critical region

df1 <- posterior_samples(mrcv_int, pars= c("b") ) %>% 
  mutate(gram_effect = exp(b_Intercept + b_gram) - exp(b_Intercept - b_gram),
         numInt_effect = exp(b_Intercept + b_int) - exp(b_Intercept - b_int),
         inter_effect = exp(b_Intercept + b_gramxint) - exp(b_Intercept - b_gramxint))

color_scheme_set("gray")
rcv_densityPlot<-mcmc_areas(
 df1,
  pars = c("inter_effect", "numInt_effect", "gram_effect"),
  prob = 0.95,
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(
    labels = c("interference ×\ngrammaticality", "interference", "grammaticality")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(title = "Main effects and interaction",
       subtitle = "Critical region") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))
```

```{r}
# Posterior probability distributions of interference effects in the critical region for grammatical and ungrammatical sentences separately

df2<-posterior_samples(mrcv_nested, pars= c("b") ) %>%
  mutate(numEff_g = exp(b_Intercept + b_int_g) - exp(b_Intercept - b_int_g),
         numEff_u = exp(b_Intercept + b_int_u) - exp(b_Intercept - b_int_u))
 
color_scheme_set("gray")
rcv_nestedPlot<-mcmc_areas(
  df2,
  pars = c("numEff_u", "numEff_g"),
  prob = 0.95, # 80% intervals
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(labels = c("ungrammatical", "grammatical")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(title = "Nested comparisons",
       subtitle = "Interference in critical region") +
  bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))
```

```{r}
# Posterior probability distributions of main effects and interaction in the post-critical region

df3<-posterior_samples(mrcadv1_int, pars= c("b") ) %>%
  mutate(gram_effect = exp(b_Intercept + b_gram) - exp(b_Intercept - b_gram),
         numInt_effect = exp(b_Intercept + b_int) - exp(b_Intercept - b_int),
         inter_effect = exp(b_Intercept + b_gramxint) - exp(b_Intercept - b_gramxint))

color_scheme_set("gray")
rcadv1_densityPlot<-mcmc_areas(
 df3,
  pars = c("inter_effect", "numInt_effect", "gram_effect"),
  prob = 0.95, # 80% intervals
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(labels = c("interference ×\ngrammaticality", "interference", "grammaticality")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(x = "Estimates [ms]", 
       title = "Main effects and interaction",
       subtitle = "Post-critical region") +
  bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +

  theme(plot.title = element_text(face="bold"))
```

```{r}
# Posterior probability distributions of interference effects in the post-critical region for grammatical and ungrammatical sentences separately

df4<-posterior_samples(mrcadv1_nested, pars= c("b") ) %>%
  mutate(numEff_g = exp(b_Intercept + b_int_g) - exp(b_Intercept - b_int_g),
         numEff_u = exp(b_Intercept + b_int_u) - exp(b_Intercept - b_int_u))
 
color_scheme_set("gray")
rcadv1_nestedPlot<-mcmc_areas(
  df4,
  pars = c("numEff_u", "numEff_g"),
  prob = 0.95, # 80% intervals
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(labels = c("ungrammatical", "grammatical")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(x = "Estimates [ms]", 
      title = "Nested comparisons",
       subtitle = "Interference in post-critical region") +
  bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold"))

```

```{r fig.width=8, fig.height=8}
spr1Density_trial <- ggarrange(rcv_densityPlot, 
                               rcadv1_densityPlot + 
                                    theme(axis.text.y = element_blank(),
                                    axis.ticks.y = element_blank(),
                                    axis.title.x = element_blank()),
                               rcv_nestedPlot, 
                               rcadv1_nestedPlot + 
                                    theme(axis.text.y = element_blank(),
                                    axis.ticks.y = element_blank(),
                                    axis.title.x = element_blank()), 
                               nrow =2, ncol = 2, align="hv",
                               labels = c("A", "B", "C", "D"), 
                               font.label = list(size=14, family ="sans"))


annotate_figure(spr1Density_trial,
              bottom = text_grob("Estimates [ms]", size = 12, family="sans"))

ggsave("spr1Density.pdf", device = "pdf", width = 190, height = 190, units = "mm")
```
