---
title: "Experiment 1 (forced-choice task)"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: pdf_document

---

\large{R code to reproduce the analysis of Experiment 1 reported in the manuscript \emph{"Does case marking affect agreement attraction in comprehension?"}.}

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.path='figures/fig-',
               fig.align='center',
               fig.show='hold',warning=FALSE,message=FALSE, echo = FALSE)

```


```{r load_data}
# Load packages
library(dplyr)
library(knitr)
library(kableExtra)
library(brms)
library(MASS)
library(ggplot2)
library(binom)
library(boot) # for backtransformations
library(ggpubr)
library(brmstools)
library(rstanarm)
library(bayesplot)
library(gridExtra) # for assembling multiple plots on one page

# Define functions
# Function to calculate standard error.
se <- function(x) {
    return(sqrt(var(x,na.rm=TRUE)/length(na.omit(x))))
}


# Function to calculate binomial standard error.
se.bin <- function(x){
  n.success = sum(na.omit(x)) #x is coded as 1 (success) or 0 (failure), so number of successes is the sum of x = 1 
  n         = length(na.omit(x))
  p         = n.success / n
  return(sqrt(p*(1-p)/n))
}

# Load data
data <- read.csv("E1_data.csv", encoding="UTF-8", header=T)
data$Participant<-as.integer(factor(data$Participant,
                                    levels=unique((data$Participant))))
```

# Participants 
***Participant exclusion.*** In total 189 participants were recruited, but data from 14 participants were excluded, resulting in 175 participants whose data were included in the analysis.

* Five participants missed the response deadline (i.e., timeout in all trials)
* Four participants reported bad vision
* Three participants reported a speech impairment
* One participant did not have Armenian as his/her L1
* One participant had filler accuracy below 70%

```{r}
# Exclude participants
data<-subset(data, Vision!="bad" & Impairment!="yes" & L1!="russian")
data<-subset(data, !(Participant %in% c(66, 68, 121, 132, 189,137))) 
```

***Demographic data.*** Below is the summary of demographic data after 14 participants were excluded. "Hand" stands for "Handedness", "Impairment" stands for "Language Impairment". As to the "Keypress", 89 participants pressed the "F" key to choose a singular verb form and the "J" key to choose a plural verb form, whereas 86 participants used the reverse key configuration.
```{r}
# Summarize demographic data
demographic <- data[!duplicated(data$Participant),] # leave one row per participant
demographicRel <- demographic[c(8:11,16:18)] # select columns with relevant info

options(knitr.kable.NA = '') # exclude NAs in the table
kable(summary(demographicRel), 
  booktabs=T, 
  caption = "Summary of participants' demographic characteristics.")  %>%
  kable_styling(latex_options = c("basic", "scale_down", "hold_position")) %>% 
  row_spec(0,bold=TRUE) 

```


```{r subset_data}
## Subset data and convert Item and Participant to factor
data$Participant<-factor(data$Participant)
data$Item<-factor(as.character(data$Item), exclude="NULL")

filler <- subset(data, grepl("^f", data$Type)) # subset filler items
target <- subset(data, grepl("a|b|c|d", data$Type)) # subset experimental items
target$Type<-factor(target$Type,levels=letters[1:4]) 
```

 
```{r data_summary, eval=FALSE}
summary(data[,-5]) # exclude the column w/Armenian characters to prevent execution error

```

# Contrast coding 
***Main effects and interaction***
```{r echo=TRUE}
# Contrasts to evaluate the main effects of case, attractor number ('num'),
# and their interaction
##         a   b   c   d
#case     -1  -1   1   1   # case match is -1, mismatch is 1
#num      -1   1  -1   1   # singular attractor is -1, plural is 1
target$case<-ifelse(target$Type%in%c("a","b"),-1,1)
target$num<-ifelse(target$Type%in%c("a","c"),-1,1)
target$casexnum<-target$case*target$num
```

\newpage

***Nested comparisons***
```{r echo=TRUE}
# Contrasts to evaluate the attractor number effects separately in case match 
# (nominative attractor) and mismatch (accusative attractor) conditions 
##          a   b   c   d
#case      -1  -1   1   1   # case match is -1, mismatch is 1
#attr_nom  -1   1   0   0   # singular attractor is -1, plural is 1  
#attr_acc   0   0  -1   1
target$attr_nom<-ifelse(target$Type=="a",-1,ifelse(target$Type=="b",1,0))
target$attr_acc<-ifelse(target$Type=="c",-1,ifelse(target$Type=="d",1,0))
```

# Filler accuracy 
* Missed responses in the filler items constitute 1%.
```{r}
sum(is.na(filler$Accuracy))[1]/dim(filler)[1]
```

\vspace{0.5cm}

* Overall accuracy (%) for the filler items
```{r}
filler %>% dplyr::summarize(
  fillerAccuracy = round(100*mean(Accuracy, na.rm = TRUE), digits=1),
  fillerSE = round(100*se.bin(Accuracy), digits=1))
```

\vspace{0.5cm}

```{r fig.height=4, fig.width=7}
# Compute mean accuracy for each participant for the filler items
filler_acc_bySubj <- filler %>% 
  group_by(Participant) %>% 
  summarize(Filler_accuracy = round(100 *mean(Accuracy, na.rm = TRUE), digits = 0))

# range(filler_acc_bySubj$Filler_accuracy) 

filler_acc_bySubj$Participant<-as.numeric(as.character
                                          (filler_acc_bySubj$Participant))

# Plot mean accuracy for each participant for the filler items 
ggplot(
  filler_acc_bySubj,
  aes(x = Participant,
      y = Filler_accuracy )) +
  geom_point() +
  scale_x_continuous(name="Participants", breaks=seq(1,189,8)) +
  ylab("Accuracy (%)") -> bySubj_fillerPlot 

# Add titles
bySubj_fillerPlot + labs(
  title = "Mean accuracy per participant for the filler items",
  subtitle = "Accuracy ranges from 74% to 100%")

```

\newpage

# Target accuracy 
* Each condition has 2100 observations of which missed responses constitute:
    + a. case match, singular attractor    - 20 NAs (0.95%) 
    + b. case match, plural attractor      - 33 NAs (1.57%)
    + c. case mismatch, singular attractor - 14 NAs (0.67%)
    + d. case mismatch, plural attractor   - 27 NAs (1.29%)
    
```{r include=FALSE}
as.data.frame(allObservations <- target %>% 
                group_by(Type) %>% 
                summarize(length = length (Type)))

as.data.frame(withoutNA<-target %>% 
                filter(Accuracy != "NA") %>% 
                group_by(Type) %>% 
                summarize(length = length (Type)))

(allObservations-withoutNA)/allObservations # percentage of NAs in each condition

```

\vspace{0.5cm}

* The NAs (missed responses) and the response times (RTs) below 200ms are excluded, resulting in the removal of 1.49% of the raw data.
```{r}
trgTrm<-subset(target, RT!="NA" & Accuracy!='NA' & RT>200)
(dim(target)[1]-dim(trgTrm)[1])/dim(target)[1]
```

\vspace{0.5cm} 

* Overall accuracy (%) for the experimental items
```{r}
trgTrm %>% dplyr::summarize(
  trgAccuracy = round(100*mean(Accuracy, na.rm = TRUE), digits=1),
  trgSE = round(100*se.bin(Accuracy), digits=1))
```

\vspace{0.5cm}

```{r}
# Compute mean accuracy for each condition for the experimental items
target_acc_byCond <-trgTrm %>% group_by(Type) %>% summarize(
  trgAccuracy = round(100 *mean(Accuracy), digits = 1),
  trgSE =  round(100*se.bin(Accuracy), digits=1))

colnames(target_acc_byCond) <- c("Condition", "Accuracy [%]", "SE")
rownames(target_acc_byCond) <- c("case match, singular attractor",
                                 "case match, plural attractor",
                                 "case mismatch, singular attractor",
                                 "case mismatch, plural attractor")

# Present mean accuracy for each condition in a table
target_acc_byCond %>%
  kable(align="c", booktabs = T, 
        caption = "Mean accuracy per condition for the experimental items") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "20em")

```

```{r fig.height=4, fig.width=7}
# Compute mean accuracy for each participant for the experimental items
target_acc_bySubj <- trgTrm %>% group_by(Participant) %>% summarize(target_accuracy = round(100 *mean(Accuracy), digits = 0))

target_acc_bySubj$Participant <- as.numeric(as.character
                                            (target_acc_bySubj$Participant))

# Plot mean accuracy for each participant for the experimental items
bySubj_targetPlot <- ggplot(target_acc_bySubj, 
       aes(x = Participant, y = target_accuracy )) + 
  geom_point() +
  scale_x_continuous(name="Participants", breaks=seq(1,189,8)) +
  ylab("Accuracy (%)") 

# Add titles
bySubj_targetPlot + labs(
  title = "Mean accuracy per participant for the experimental items",
  subtitle = "Accuracy ranges from 47% to 100%")

```

# Response time data 
```{r}
rtCorrect<-subset(trgTrm, Accuracy==1) # include only correctly-answered trials
```

```{r}
# Create RT boxplots
op<-par(mfrow=c(1,2) ,pty="m")

boxplot(RT~Type, rtCorrect, col=c("grey","black"), 
        border="brown", notch=TRUE, 
        main="Raw response times")

boxplot(log(RT)~Type, rtCorrect, col=c("grey","black"), 
        border="brown", notch=TRUE, 
        main="Logged response times")
```

```{r}
# Compute mean RT for each conditions in trials on which a correct answer was provided  
rt_byCond<-rtCorrect %>% 
  group_by(Type) %>% 
  summarize(rtMean = round(mean(RT), digits = 0),
  rtSE = round(se(RT), digits = 0))

colnames(rt_byCond) <- c("Condition", "Mean RT [ms]", "SE")
rownames(rt_byCond) <- c("case match, singular attractor",
                                 "case match, plural attractor",
                                 "case mismatch, singular attractor",
                                 "case mismatch, plural attractor")

# Present mean RT for each condition in a table
 rt_byCond %>%
   kable(align="c", booktabs = T,
         caption = "Mean response time per condition. We have only considered the trials on which correct answers were provided.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) %>%
  column_spec(1, width = "20em")
```

\newpage

# Priors 
```{r echo=TRUE}
# Priors for accuracy analysis involving main effects and interaction
priors_acc_two_way <- c(set_prior("normal(0,10)", class="Intercept"),
                 set_prior("normal(0,1)", class="b", coef="case"),
                 set_prior("normal(0,1)", class="b", coef="num"),
                 set_prior("normal(0,1)", class="b", coef="casexnum"),
                 set_prior("normal(0,1)", class="sd"),
                 set_prior("lkj(2)", class="cor"))

# Priors for response time analysis involving main effects and interaction
priors_rt_two_way <- c(set_prior("normal(0,10)", class="Intercept"),
                 set_prior("normal(0,1)", class="b", coef="case"),
                 set_prior("normal(0,1)", class="b", coef="num"),
                 set_prior("normal(0,1)", class="b", coef="casexnum"),
                 set_prior("normal(0,1)", class="sd"),
                 set_prior("normal(0,1)", class="sigma"),
                 set_prior("lkj(2)", class="cor"))
```

```{r echo=TRUE}
# Priors for accuracy analysis involving nested comparisons
priors_acc_nested<- c(set_prior("normal(0,10)", class="Intercept"),
           set_prior("normal(0,1)", class="b", coef="case"),
           set_prior("normal(0,1)", class="b", coef="attr_nom"),
           set_prior("normal(0,1)", class="b", coef="attr_acc"),
           set_prior("normal(0,1)", class="sd"),
           set_prior("lkj(2)", class="cor"))

# Priors for response time analysis involving nested comparisons
priors_rt_nested<- c(set_prior("normal(0,10)", class="Intercept"),
           set_prior("normal(0,1)", class="b", coef="case"),
           set_prior("normal(0,1)", class="b", coef="attr_nom"),
           set_prior("normal(0,1)", class="b", coef="attr_acc"),
           set_prior("normal(0,1)", class="sd"),
           set_prior("normal(0,1)", class="sigma"),
           set_prior("lkj(2)", class="cor"))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for accuracy data to evaluate main effects of case, attractor number, and their interaction
macc_int <- brm(formula = Accuracy ~ case+num+casexnum+
                 (1+case+num+casexnum|Participant) + 
                 (1+case+num+casexnum|Item),
                 data = trgTrm, family = bernoulli(), prior = priors_acc_two_way,
                 iter = 2000, chains = 4, control = list(adapt_delta = 0.99))

```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for accuracy data, with nested comparisons to evaluate attractor number effect for the case match and mismatch conditions separately
macc_nested <- brm(formula = Accuracy ~ case+attr_nom+attr_acc + (1+case+attr_nom+attr_acc|Participant) + (1+case+attr_nom+attr_acc|Item),
                 data = trgTrm, family = bernoulli(), prior = priors_acc_nested,
                 iter = 2000, chains = 4, control = list(adapt_delta = 0.99))
```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for response time data to evaluate main effects of case, attractor number, and their interaction
mrt_int <- brm(formula = log(RT) ~ case+num+casexnum+
                 (1+case+num+casexnum|Participant) + 
                 (1+case+num+casexnum|Item),
                 data = rtCorrect, family = gaussian(), prior = priors_rt_two_way,
                 iter = 2000, chains = 4, control = list(adapt_delta = 0.99))

```

```{r include=FALSE, cache=TRUE, cache.comments=FALSE}
# Run model for response time data, with nested comparisons to evaluate attractor number effect for the case match and mismatch conditions separately
mrt_nested <- brm(formula = log(RT) ~ case+attr_nom+attr_acc+ (1+case+attr_nom+attr_acc|Participant) + (1+case+attr_nom+attr_acc|Item),
                 data = rtCorrect, family = gaussian(), prior = priors_rt_nested,
                 iter = 2000, chains = 4, control = list(adapt_delta = 0.99))

```

\newpage

# Accuracy analysis results 
In the tables below, each effect is described in terms of its posterior mean on log odds scale and the lower and upper bound of 95% credible interval.
```{r}
# summarize model output in a table
kable(fixef(macc_int), booktabs=T, caption = "Model output for accuracy analysis examining main effects of case, attractor number ('num), and their interaction.")%>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to percentages***
```{r}

posterior_samples(macc_int, pars= c("b") ) %>%
  mutate(pred = inv.logit(b_Intercept + b_case) - inv.logit(b_Intercept - 
                                                       b_case))  %>%
  summarize(Estimate_case = round(100*mean(pred),1) %>% paste("%"),
            `95% CrI` = paste(round(100*quantile(pred,c(0.025,.975)),1), 
                                collapse=", ") %>%
              paste0("[",.,"]"))
 #----------------------------------------------------#

posterior_samples(macc_int, pars= c("b") ) %>%
  mutate(pred = inv.logit(b_Intercept + b_num) - inv.logit(b_Intercept - 
                                                       b_num))  %>%
  summarize(Estimate_num = round(100*mean(pred),1) %>% paste("%"),
            `95% CrI` = paste(round(100*quantile(pred,c(0.025,.975)),1), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

 #----------------------------------------------------#

posterior_samples(macc_int, pars= c("b") ) %>%
  mutate(pred = inv.logit(b_Intercept + b_casexnum) - inv.logit(b_Intercept - 
                                                       b_casexnum))  %>%
  summarize(Estimate_casexnum = round(100*mean(pred),1) %>% paste("%"),
            `95% CrI` = paste(round(100*quantile(pred,c(0.025,.975)),1), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

```

```{r}
# summarize model output in a table
kable(fixef(macc_nested), booktabs=T, caption = "Model output for accuracy analysis examining attractor number effect (i.e., attraction effect) for the case match (nominative attractor; attr\\_nom) and case mismatch (accusative attractor; attr\\_acc) conditions separately.")%>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to percentages***
```{r}

posterior_samples(macc_nested, pars= c("b") ) %>%
  mutate(pred = inv.logit(b_Intercept + b_attr_nom) - inv.logit(b_Intercept - 
                                                       b_attr_nom))  %>%
  summarize(Estimate_attraction_caseMatch = round(100*mean(pred),1) %>% paste("%"),
            `95% CrI` = paste(round(100*quantile(pred,c(0.025,.975)),1), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

 #----------------------------------------------------#

posterior_samples(macc_nested, pars= c("b") ) %>%
  mutate(pred = inv.logit(b_Intercept + b_attr_acc) - inv.logit(b_Intercept - 
                                                       b_attr_acc))  %>%
  summarize(Estimate_attraction_caseMismatch = round(100*mean(pred),1) %>% paste("%"),
            `95% CrI` = paste(round(100*quantile(pred,c(0.025,.975)),1), 
                                collapse=", ") %>%
              paste0("[",.,"]"))
```

\newpage

# Response time analysis results 
Only response times for correctly-answered trials have been included in the analysis. In the tables below, each effect is described in terms of its posterior mean on log scale and the lower and upper bound of 95% credible interval.
```{r}
# summarize model output in a table
kable(fixef(mrt_int), 
      booktabs=T, 
      caption = "Model output for response time analysis examining main effects of case, attractor number ('num'), and their interaction.") %>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrt_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_case) - exp(b_Intercept - 
                                                       b_case))  %>%
  summarize(Estimate_case = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))
 
#----------------------------------------------------#

posterior_samples(mrt_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_num) - exp(b_Intercept - 
                                                       b_num))  %>%
  summarize(Estimate_num = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrt_int, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_casexnum) - exp(b_Intercept - 
                                                       b_casexnum))  %>%
  summarize(Estimate_casexnum = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))
```

```{r}
# summarize model output in a table
kable(fixef(mrt_nested), booktabs=T, caption = "Model output for response time analysis examining attractor number effect (i.e., attraction effect) for the case match (nominative attractor; attr\\_nom) and case mismatch (accusative attractor; attr\\_acc) conditions separately.")%>%
  kable_styling(full_width = T, latex_options = "hold_position") %>% 
  row_spec(0,bold=TRUE) 
```

***Model estimates back-transformed to milliseconds***
```{r}
posterior_samples(mrt_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_attr_nom) - exp(b_Intercept - 
                                                       b_attr_nom))  %>%
  summarize(Estimate_attraction_caseMatch = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))

#----------------------------------------------------#

posterior_samples(mrt_nested, pars= c("b") ) %>%
  mutate(pred = exp(b_Intercept + b_attr_acc) - exp(b_Intercept - 
                                                       b_attr_acc))  %>%
  summarize(Estimate_attraction_caseMismatch = mean(pred) %>%
              round %>% paste("ms"),
            `95% CrI` = paste(round(quantile(pred,c(0.025,.975)),0), 
                                collapse=", ") %>%
              paste0("[",.,"]"))
```

\newpage
\blandscape

# Plots 
```{r}
# Plot mean accuracy in each of the four conditions
trgTrm %>%
  group_by(Type) %>%
  summarize(
    mean.acc = 100*mean(Accuracy),
    se.lower = mean.acc - 100*(se.bin(Accuracy)),
    se.upper = mean.acc + 100*(se.bin(Accuracy))) -> df_Acc

df_Acc$Case<-ifelse(df_Acc$Type    %in% c("a","b"), "case match", "case mismatch")
df_Acc$Number <-ifelse(df_Acc$Type %in% c("a","c"), "singular", "plural")

## Change the factor level order
df_Acc$Case <- factor(df_Acc$Case, levels=c("case match", "case mismatch")) 
df_Acc$Number <- factor(df_Acc$Number, levels = c("singular","plural"))

plotAcc <- ggplot(
  data =df_Acc,
  aes(x=Case, y=mean.acc, group=Number, color=Number)) +
  geom_errorbar(aes(ymin=se.lower, ymax=se.upper),
                width=0.1,size=.4, 
                show.legend = FALSE) + 
  geom_line(aes(linetype=Number),size=.4) +
  geom_point(size=2, show.legend = FALSE) +
  scale_y_continuous(labels = scales::number_format(accuracy = 1)) +
  scale_color_manual(values = alpha(c("grey30", "grey30")))+
  theme_bw(base_size = 12, base_family = "sans") +
  labs(y = "[%]",
       title = "Accuracy") +
  labs(group="Attractor number",
       linetype="Attractor number", 
       color="Attractor number") +
  theme(plot.title = element_text(face="bold"),
        axis.title.x=element_blank(),
        legend.position="bottom",
        legend.key.width = unit(0.8,"cm")) 

```

```{r}
# Plot mean response latency in each of the four conditions
rtCorrect %>%
  group_by(Type) %>%
  dplyr::summarize(
    mean.rt = mean(RT),
    se.lower = mean.rt - se(RT),
    se.upper = mean.rt + se(RT),
    ci.lower = mean.rt - 2*se(RT),
    ci.upper = mean.rt + 2*se(RT)) -> df_RT

df_RT$Case<-ifelse(df_RT$Type    %in% c("a","b"), "case match", "case mismatch")
df_RT$Number <-ifelse(df_RT$Type %in% c("a","c"), "singular", "plural")

## Change the factor level order
df_RT$Case <- factor(df_RT$Case, levels=c("case match", "case mismatch")) 
df_RT$Number <- factor(df_RT$Number, levels = c("singular","plural"))

plotRT <- ggplot(data = df_RT,
              aes(x = Case, 
                  y= mean.rt, group = Number, 
                  color = Number)) +
  geom_errorbar(aes(ymin = se.lower, ymax = se.upper),
                width=.1,size=.4, show.legend=FALSE) +
  geom_line(aes(linetype = Number), size=.4) +
  geom_point(size=2, show.legend = FALSE) +
  geom_line(aes(linetype = Number), size=.4) +
  scale_color_manual(values = alpha(c("grey30", "grey30")))+
  theme_bw(base_size = 12, base_family = "sans") +
  labs(y = "[ms]",
       title = "Response time")+
  theme(legend.position="bottom")+
  labs(
    group="Attractor number",
    linetype="Attractor number",
    color="Attractor number") +
  theme(plot.title = element_text(face = "bold"),
             axis.title.x = element_blank()) 
       

# grid.arrange(plotAcc, plotRT, ncol=2)
```

```{r fig.width=10, fig.height=5}
ggarrange(plotAcc, plotRT,  ncol = 2, align = "h", labels = c("A", "B"), common.legend = TRUE, legend = "bottom", font.label = list(size=14, family ="sans"))

ggsave("ibexBarPlots.pdf", device = "pdf", width = 190, height = 95, units = "mm")
```

```{r}
# Plot posterior probability distributions of accuracy effects
df1 <- posterior_samples(macc_int, pars= c("b") ) %>%
  mutate(case_effect = inv.logit(b_Intercept + b_case) - inv.logit(b_Intercept - b_case),
         num_effect = inv.logit(b_Intercept + b_num) - inv.logit(b_Intercept - b_num),
         inter_effect = inv.logit(b_Intercept + b_casexnum) - inv.logit(b_Intercept - b_casexnum))  

color_scheme_set("gray")
mcmc_areas(
 df1,
  pars = c("inter_effect", "num_effect", "case_effect"),
  prob = 0.95,
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(labels = c("case ×\n number", "number", "case")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(x = "Estimates [proportions]",
       title = "Accuracy analysis") +
  bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold")) +
  scale_x_continuous(breaks=seq(-0.08,0.02, by=0.02),
                     limits = c(-0.07,0.02),
                     labels = function(x) round(as.numeric(x), digits=2)) -> density_acc_int
```

```{r}
# Plot posterior probability distributions of RT effects
df2<-posterior_samples(mrt_int, pars= c("b") ) %>%
  mutate(case_effect = exp(b_Intercept + b_case) - exp(b_Intercept - b_case),
         num_effect = exp(b_Intercept + b_num) - exp(b_Intercept - b_num),
         inter_effect = exp(b_Intercept + b_casexnum) - exp(b_Intercept - b_casexnum))

color_scheme_set("gray")
mcmc_areas(
 df2,
  pars = c("inter_effect", "num_effect", "case_effect"),
  prob = 0.95, 
  prob_outer = 0.99, 
  point_est = "mean") +
  ggplot2::scale_y_discrete(labels = c("case ×\n attractor number", 
                                       "attractor number", "case")) +
  geom_vline(xintercept=0, linetype="dashed", color="red", size=.5) +
  labs(x = "Estimates [ms]",
       title = "Response time analysis") +
bayesplot::theme_default(base_family = getOption("bayesplot.base_family", "sans"),
                         base_size = getOption("bayesplot.base_size", 12)) +
  theme(plot.title = element_text(face="bold")) -> density_rt_int

```

```{r fig.width=10, fig.height=5}
ggarrange(density_acc_int, 
                        density_rt_int +
                        theme(axis.text.y = element_blank(),
                        axis.ticks.y = element_blank()),
                        ncol = 2, align = "hv",
                        labels = c("A", "B"), 
                        font.label = list(size=14, family ="sans")) 

ggsave("ibexDensityPlots.pdf", device = "pdf", width = 190, height = 95, units = "mm")
```

\elandscape